Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-08 ms.tex
add Dunlap acknowledgment

Like the official WISE Atlas coadds, unWISE processing divides the sky
into a set of 18240 1.56$^{\circ}$$\times$1.56$^{\circ}$ tiles
arranged along iso-declination rings. Whereas the Atlas images
are smoothed by the WISE PSF, the unWISE code uses Lanczos interpolation to 
preserve the native WISE angular resolution during coaddition, creating stacked
outputs which are 2048 pixels on a side, with 2.75$''$ pixels.

@@

This research is supported by the Director, Office of Science, Office of High 
Energy Physics of the U.S. Department of Energy under Contract No. 
DE–AC02–05CH1123, and by the National Energy Research Scientific Computing 
Center, a DOE Office of Science User Facility under the same contract; 
additional support for DESI is provided by the U.S. National Science
Foundation, Division of Astronomical Sciences under Contract No. AST-0950945 to
the National Optical Astronomy Observatory; the Science and Technologies 
Facilities Council of the United Kingdom; the Gordon and Betty Moore 
Foundation; the Heising-Simons Foundation; and by the DESI Member Institutions.

>>>>

Like the official WISE Atlas coadds, unWISE processing divides the sky
into a set of 18,240 1.56$^{\circ}$$\times$1.56$^{\circ}$ tiles
arranged along iso-declination rings. Whereas the Atlas images
are smoothed by the WISE PSF, the unWISE code uses Lanczos interpolation to 
preserve the native WISE angular resolution during coaddition, creating stacked
outputs which are 2048 pixels on a side, with 2.75$''$ pixels.

@@

This research is supported by the Director, Office of Science, Office of High 
Energy Physics of the U.S. Department of Energy under Contract No. 
DE–AC02–05CH1123, and by the National Energy Research Scientific Computing 
Center, a DOE Office of Science User Facility under the same contract; 
additional support for DESI is provided by the U.S. National Science
Foundation, Division of Astronomical Sciences under Contract No. AST-0950945 to
the National Optical Astronomy Observatory; the Science and Technologies 
Facilities Council of the United Kingdom; the Gordon and Betty Moore 
Foundation; the Heising-Simons Foundation; and by the DESI Member Institutions.
The Dunlap Institute is funded through an endowment established by the David 
Dunlap family and the University of Toronto.
